Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-04-07 DGMM2025/paper.tex
removing the ghost package

\usepackage{changes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
\usepackage{algc}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    \begin{algorithm}
        \caption{Given a cell complex C and a radius \(r\), compute the visibility at every point of C up to distance \(r\).}
        \label{alg:visibility}
        \begin{algorithmic}

            \Function{Translation}{$I$: Interval, L: Intervals}
                \State $[a, b] \gets I$
                \State $Result \gets \emptyset$
                \For{each interval $J$ in L}
                    \State $[c, d] \gets J$
                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
                        \State $Result \gets Result \cup [c-a,d-b]$
                    \EndIf
                \EndFor
                \State \Return Result
            \EndFunction

@@

    \begin{algorithm}
        \caption{Given 2 lists of intervals K and L, find $K \cup L$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
                \State $R \gets \emptyset$
                \State $k, l \gets 0$
                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                    \State $[a,b] \gets K[k]$
                    \State $[c,d] \gets L[l]$
                    \State $cMin \gets max(a, c)$
                    \State $cMax \gets max(b, d)$
                    \If{$cMax < cMin$}
                        \State $R.append([cMin, cMax])$
                    \EndIf
                    \If{$a \leq d$}
                        \State $k \gets k+1$
                    \EndIf
                    \If{$c \leq b$}
                        \State $l \gets l+1$
                    \EndIf
                \EndWhile
                \State \Return $R$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}

>>>>

\usepackage{changes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    \begin{algorithm}
        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$.}
        \label{alg:visibility}
        \begin{algorithmic}
            \Function{Translation}{I: Interval, L: Intervals}
                \State $[a, b] \gets I$
                \State $Result \gets \emptyset$
                \For{each interval $J$ in L}
                    \State $[c, d] \gets J$
                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
                        \State $Result \gets Result \cap [c-a,d-b]$
                    \EndIf
                \EndFor
                \State \Return Result
            \EndFunction

@@

    \begin{algorithm}
        \caption{Given 2 lists of intervals K and L, find $K \cap L$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
                \State $R \gets \emptyset$
                \State $k, l \gets 0$
                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                    \State $[a,b] \gets K[k]$
                    \State $[c,d] \gets L[l]$
                    \State $cMin \gets max(a, c)$
                    \State $cMax \gets max(b, d)$
                    \If{$cMax < cMin$}
                        \State $R.append([cMin, cMax])$
                    \EndIf
                    \If{$a \leq d$}
                        \State $k \gets k+1$
                    \EndIf
                    \If{$c \leq b$}
                        \State $l \gets l+1$
                    \EndIf
                \EndWhile
                \State \Return $R$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}
